Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-03-25 tex/MesnardoBarba2019.tex
Add sentences about the cost

Although the two-dimensional simulations gave us some insights into to flow dynamics happening in the behind the snake, we know that at this Reynolds number ($Re = 2000$), three-dimensional will develop in the wake.
Thus, we submitted jobs to Azure Batch to compute the three-dimensional flow around a cylinder with the same anatomically accurate cross-section.
The computational domain is extended in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (uniform discretization in the $z$-direction; see Table \ref{tab:grid_specs}).
The grid is kept uniform in the $z$-direction and we enforce periodic conditions at the front and back boundaries.
The simulation ran in a Docker container on Azure Batch using Batch Shipyard.
The job was submitted to a pool of two \texttt{NC24r} nodes using $24$ MPI processes and $4$ GPU devices per node.
The task completed $100,000$ time steps ($100$ time units with a time-step size $\Delta t = 0.01 c / U_\infty$) in about $5$ days and $16$ hours.

@@

% Mention the 7-day limitation for jobs with Azure Batch.
% Mention that Batch Shipyard can pull images from public and private registries.
% Mention that Singularity containers are also supported in Batch Shipyard.

\begin{table*}[!h]
    \renewcommand{\arraystretch}{1.5}
    \caption{NC series on Microsoft Azure. (Prices as of May 13, 2018.)}
    \label{tab:nc_series}
    \centering
    \begin{tabular}{cccccccc}
        Instance & cores & RAM & disk sizes & GPU & pay-as-you-go & 1-year reserved & 3-year reserved \\
        && (GiB) & (Gib) && (\$/hr) & (\$/hr) & (\$/hr) \\
        \hline
        NC6 & 6 & 56 & 340 & 1 x K80 & 0.90 & 0.574 & 0.40 \\
        NC12 & 12 & 112 & 680 & 2 x K80 & 1.80 & 1.147 & 0.80 \\
        NC24 & 24 & 224 & 1,440 & 4 x K80 & 3.60 & 2.294 & 1.599 \\
        NC24r\footnotemark & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 2.523 & 1.758 \\
        \hline
    \end{tabular}
\end{table*}
\footnotetext{NC24r instances are RDMA (Remote Direct Access Memory) capable with InfiniBand network.}

>>>>

Although the two-dimensional simulations gave us some insights into to flow dynamics happening in the behind the snake, we know that at this Reynolds number ($Re = 2000$), three-dimensional will develop in the wake.
Thus, we submitted jobs to Azure Batch to perform direct numerical simulation of the three-dimensional flow around a cylinder with the same anatomically accurate cross-section.
The computational domain is extended in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (uniform discretization in the $z$-direction; see Table \ref{tab:grid_specs}).
The grid is kept uniform in the $z$-direction and we enforce periodic conditions at the front and back boundaries.
The simulation ran in a Docker container on Azure Batch using Batch Shipyard.
The job was submitted to a pool of two \texttt{NC24r} nodes using $24$ MPI processes and $4$ GPU devices per node.
The task completed $100,000$ time steps ($100$ time units with a time-step size $\Delta t = 0.01 c / U_\infty$) in about $5$ days and $16$ hours.

@@

% Mention the 7-day limitation for jobs with Azure Batch. (WARNING: according to the Batch Shipyard documentation, tasks can have a maximum lifetime of 180 days.)
% Mention that Batch Shipyard can pull images from public and private registries.
% Mention that Singularity containers are also supported in Batch Shipyard.

For the year $2018$, Microsoft Azure granted our research lab a sponsorship of $20,000$ USD in cloud credits to run CFD simulations with our in-house software.
From May to December, we spend a total of $20,614$ USD to run simulations of the gliding snake.
During that period, we have been charged data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges are due the usage of virtual machines.
We had the opportunity to use different instances on Microsoft Azure and most the charges for the usage of virtual machines of the \texttt{NC24r} instance (used for the two- and three-dimensional simulations of the flying snake).
The \texttt{NC24r} instance is part of the NC-series (Table \ref{tab:nc_series}); we copiously used as it enables RDMA capabilities for our MPI application and features NVIDIA K80 GPU devices.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).

\begin{table}
    \renewcommand{\arraystretch}{1.5}
    \caption{Charges incurred for the usage of different services on Microsoft Azure.}
    \label{tab:azure_charges}
    \centering
    \begin{tabular}{cll}
        Service name & Cost (USD) & \% of total cost \\
        \hline
        Bandwidth & $46.85$ & $0.23$ \\
        Data Management & $0.56$ & $0.003$ \\
        Networking & $1.38$ & $0.007$ \\
        Storage & $25.93$ & $0.16$ \\
        Virtual Machines & $20,582.64$& $99.6$ \\
        \hline
        Total & $20,614$ & \\
        \hline
    \end{tabular}
\end{table}

\begin{table*}[!h]
    \renewcommand{\arraystretch}{1.5}
    \caption{NC series on Microsoft Azure. (Prices as of March 24, 2019, for CentOS or Ubuntu Linux Virtual Machines in the East US region.)}
    \label{tab:nc_series}
    \centering
    \begin{tabular}{cccccccc}
        Instance & cores & RAM & disk sizes & GPU & pay-as-you-go & 1-year reserved & 3-year reserved \\
        && (GiB) & (Gib) && (\$/hr) & (\$/hr) & (\$/hr) \\
        \hline
        NC6 & 6 & 56 & 340 & 1 x K80 & 0.90 & 0.5733 & 0.3996 \\
        NC12 & 12 & 112 & 680 & 2 x K80 & 1.80 & 1.1466 & 0.7991 \\
        NC24 & 24 & 224 & 1,440 & 4 x K80 & 3.60 & 2.2932 & 1.5981 \\
        NC24r\footnotemark & 24 & 224 & 1,440 & 4 x K80 & 3.96 & 2.5224 & 1.7578 \\
        \hline
    \end{tabular}
\end{table*}
\footnotetext{The NC24r configuration provides a low latency, high throughput network interface optimized for tightly coupled parallel applications.}

In a new effort to make our research transparent and reproducible by others, we have version-controlled all the input files, pre- and post-processing scripts, as well as the Batch Shipyard configuration files required to rerun the simulations on Microsoft Azure.
In addition, all the scripts to reproduce the figures in the present article are made available.
The reproducibility packages are hosted on GitHub in the repository \texttt{cloud-repro}.\footnote{\url{https://github.com/barbagroup/cloud-repro}}
